Motional Ground-State Cooling Outside the Lamb-Dicke Regime -- Supplemental material

### 2018-01-29 sm.tex
WIP: Update SM

\section{Raman Sideband Cooling Pulse Parameters and Sequence}
Here, we list the full Raman sideband cooling (RSC) pulse parameters and sequence used to obtain the result in the manuscript.
A step of RSC contains a Raman pulse and an optical pumping pulse.
The full RSC sequence includes about 1000 pulses in 100 ms.

\subsection{Optical pumping parameters}
The optical pumping is performed with a $\sigma^-$-polarized beam aligned with an 8.8 G bias magnetic field.
There are two frequencies in the beam: one is on resonance with
the $|F=2,m_F=-1\rangle$ of $3^2S_{1/2}$ to $|F'=2,m_{F'}=-2\rangle$ of $3^2P_{1/2}$ D1 transition
and the other is on resonance with the $|F=1,m_F=-1\rangle$ of $3^2S_{1/2}$ to $|F'=2,m_{F'}=-2\rangle$ of $3^2P_{3/2}$ D2 transition.
All optical pumping pulses have the length of $40\,\mu$s
with a scattering rate of $0.14$ MHz for atoms in $|F=1,m_F=-1\rangle$
and a scattering rate of $0.39$ MHz for atoms in $|F=2,m_F=-1\rangle$.

\subsection{Raman pulse parameters}
Each Raman pulse in the cooling sequence is followed immediately by an optical pumping
pulse.
The full parameters for the Raman pulses, including the cooling ``axis'', the sideband ``order ($\Delta n$)'', the cooling frequency ``$\delta '$", the carrier ($\Delta n=0$) frequency ``$\delta_0'$'', the pulse ``duration'', the pulse strength in ``$\Omega_0$'', and the beam of which a non-uniform ``power ramp'' is applied,   are listed in 9 groups below.
The applied cooling frequency, $\delta'$,  is the two-photon detuning given relative to the zero-field $F=1$ and $F=2$ hyperfine splitting
of $1.7716261288(10)$GHz~\cite{SteckNa}.
%All of the relative detunings are negative indicating that the frequency difference is smaller than the zero-field hyperfine splitting. Higher-order sidebands for cooling
%A more negative number corresponds to lower order cooling sidebands
%and a more negative number corresponds to higher order ones.
Due to the Stark shifts of the Raman beams, the carrier transition, $\delta'_0$, varies with the power of the Raman beams. $\delta'_0$ is given also relative to the zero-field hyperfine splitting.
The strength of the pulses given in $\Omega_0$ determines the two-photon Rabi frequency, $\Omega_{n,\Delta n}=\Omega_0 \langle n|e^{i \vec{k} \cdot \vec{r}}|n+\Delta n\rangle$.
We adopt the convention that a $\pi$-pulse between state $n$ and $n+\Delta n$ requires a duration $\pi/\Omega_{n,\Delta n}$.
 The difference between $\delta'$ and $\delta'_0$ gives the motional sideband frequency, $\delta$.
%The full Rabi frequency is given as the two-photon Rabi frequency $\Omega$ including only electronic dipole matrix element excluding the matrix element
%from wavefunction overlap.
Many Raman pulses include a ``power ramp'' with a Blackman envelope~\cite{Kasevich1992} to minimize off-resonant excitations.
Because each Raman pulse is a product of two spatial- and temporal-overlapped laser beams, the ``power ramp'' is applied only to the beam that has the smaller light shift (we label the beam by the corresponding $F$ number) while the other beam has a square-pulse shape.
For a Raman pulse with a power ramp,
the Rabi frequency gives the arithmetic mean over the duration of the pulse.

%The power ramp field gives, if any,
%the beam (in terms of their corresponding $F$ number)
%that ramps with a Blackman profile during the pulse~\cite{Kasevich1992}.
\newpage

\subsubsection{Group 1}
This group is repeated 5 times.
\begin{center}
  \begin{tabular}{|c|c|c|c|c|c|c|}
    \hline
    Axis&$\Delta n$&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Duration ($\mu$s)& $\Omega_0$ (kHz)&Power ramp\\\hline
    $x$&-2&$-17.6375$&$-18.42$&25&$2\pi\times34$&F1\\\hline
    $y$&-2&$-17.2825$&$-18.47$&25&$2\pi\times34$&F1\\\hline
    $x$&-1&$-18.03$&$-18.42$&25&$2\pi\times34$&F1\\\hline
    $y$&-1&$-17.875$&$-18.47$&21&$2\pi\times34$&F1\\\hline
  \end{tabular}
\end{center}
\subsubsection{Group 2}
This group is repeated 5 times.
\begin{center}
  \begin{tabular}{|c|c|c|c|c|c|c|}
    \hline
    Axis&$\Delta n$&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Duration ($\mu$s)& $\Omega_0$ (kHz)&Power ramp\\\hline
    $z$&-8&$-17.966$&$-18.506$&80&$2\pi\times14$&\\\hline
    $x$&-2&$-17.6375$&$-18.42$&25&$2\pi\times34$&F1\\\hline
    $z$&-7&$-18.0335$&$-18.506$&80&$2\pi\times14$&\\\hline
    $y$&-2&$-17.2825$&$-18.47$&25&$2\pi\times34$&F1\\\hline
    $z$&-8&$-17.966$&$-18.506$&80&$2\pi\times14$&\\\hline
    $x$&-1&$-18.03$&$-18.42$&25&$2\pi\times34$&F1\\\hline
    $z$&-7&$-18.0335$&$-18.506$&80&$2\pi\times14$&\\\hline
    $y$&-1&$-17.875$&$-18.47$&21&$2\pi\times34$&F1\\\hline
  \end{tabular}
\end{center}
\subsubsection{Group 3}
This group is repeated 6 times.
\begin{center}
  \begin{tabular}{|c|c|c|c|c|c|c|}
    \hline
    Axis&$\Delta n$&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Duration ($\mu$s)& $\Omega_0$ (kHz)&Power ramp\\\hline
    $z$&-7&$-18.0335$&$-18.506$&80&$2\pi\times14$&\\\hline
    $x$&-2&$-17.6375$&$-18.42$&25&$2\pi\times34$&F1\\\hline
    $z$&-6&$-18.101$&$-18.506$&80&$2\pi\times14$&\\\hline
    $y$&-2&$-17.2825$&$-18.47$&25&$2\pi\times34$&F1\\\hline
    $z$&-7&$-18.0335$&$-18.506$&80&$2\pi\times14$&\\\hline
    $x$&-1&$-18.03$&$-18.42$&25&$2\pi\times34$&F1\\\hline
    $z$&-6&$-18.101$&$-18.506$&80&$2\pi\times14$&\\\hline
    $y$&-1&$-17.875$&$-18.47$&21&$2\pi\times34$&F1\\\hline
  \end{tabular}
\end{center}

\newpage
\subsubsection{Group 4}
This group is repeated 7 times.
\begin{center}
  \begin{tabular}{|c|c|c|c|c|c|c|}
    \hline
    Axis&$\Delta n$&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Duration ($\mu$s)& $\Omega_0$ (kHz)&Power ramp\\\hline
    $z$&-6&$-18.101$&$-18.506$&80&$2\pi\times14$&\\\hline
    $x$&-2&$-17.6375$&$-18.42$&25&$2\pi\times34$&F1\\\hline
    $z$&-5&$-18.1685$&$-18.506$&60&$2\pi\times14$&\\\hline
    $y$&-2&$-17.2825$&$-18.47$&25&$2\pi\times34$&F1\\\hline
    $z$&-6&$-18.101$&$-18.506$&80&$2\pi\times14$&\\\hline
    $x$&-1&$-18.03$&$-18.42$&25&$2\pi\times34$&F1\\\hline
    $z$&-5&$-18.1685$&$-18.506$&60&$2\pi\times14$&\\\hline
    $y$&-1&$-17.875$&$-18.47$&21&$2\pi\times34$&F1\\\hline
  \end{tabular}
\end{center}
\subsubsection{Group 5}
This group is repeated 7 times.
\begin{center}
  \begin{tabular}{|c|c|c|c|c|c|c|}
    \hline
    Axis&$\Delta n$&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Duration ($\mu$s)& $\Omega_0$ (kHz)&Power ramp\\\hline
    $z$&-5&$-18.1685$&$-18.506$&90&$2\pi\times17$&F2\\\hline
    $x$&-1&$-18.03$&$-18.42$&38&$2\pi\times34$&F1\\\hline
    $z$&-4&$-18.236$&$-18.506$&75&$2\pi\times17$&F2\\\hline
    $y$&-1&$-17.875$&$-18.47$&25&$2\pi\times34$&F1\\\hline
    $z$&-5&$-18.1685$&$-18.506$&90&$2\pi\times17$&F2\\\hline
    $x$&-1&$-18.03$&$-18.42$&43&$2\pi\times34$&F1\\\hline
    $z$&-4&$-18.236$&$-18.506$&75&$2\pi\times17$&F2\\\hline
    $y$&-1&$-17.875$&$-18.47$&28&$2\pi\times34$&F1\\\hline
  \end{tabular}
\end{center}
\subsubsection{Group 6}
This group is repeated 8 times.
\begin{center}
  \begin{tabular}{|c|c|c|c|c|c|c|}
    \hline
    Axis&$\Delta n$&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Duration ($\mu$s)& $\Omega_0$ (kHz)&Power ramp\\\hline
    $z$&-4&$-18.236$&$-18.506$&75&$2\pi\times17$&F2\\\hline
    $x$&-1&$-18.03$&$-18.42$&38&$2\pi\times34$&F1\\\hline
    $z$&-3&$-18.3035$&$-18.506$&60&$2\pi\times17$&F2\\\hline
    $y$&-1&$-17.875$&$-18.47$&25&$2\pi\times34$&F1\\\hline
    $z$&-4&$-18.236$&$-18.506$&75&$2\pi\times17$&F2\\\hline
    $x$&-1&$-18.03$&$-18.42$&43&$2\pi\times34$&F1\\\hline
    $z$&-3&$-18.3035$&$-18.506$&60&$2\pi\times17$&F2\\\hline
    $y$&-1&$-17.875$&$-18.47$&28&$2\pi\times34$&F1\\\hline
  \end{tabular}
\end{center}

\newpage
\subsubsection{Group 7}
This group is repeated 10 times.
\begin{center}
  \begin{tabular}{|c|c|c|c|c|c|c|}
    \hline
    Axis&$\Delta n$&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Duration ($\mu$s)& $\Omega_0$ (kHz)&Power ramp\\\hline
    $z$&-3&$-18.3035$&$-18.506$&60&$2\pi\times17$&F2\\\hline
    $x$&-1&$-18.03$&$-18.42$&38&$2\pi\times34$&F1\\\hline
    $z$&-2&$-18.371$&$-18.506$&60&$2\pi\times17$&F2\\\hline
    $y$&-1&$-17.875$&$-18.47$&25&$2\pi\times34$&F1\\\hline
    $z$&-3&$-18.3035$&$-18.506$&60&$2\pi\times17$&F2\\\hline
    $x$&-1&$-18.03$&$-18.42$&43&$2\pi\times34$&F1\\\hline
    $z$&-2&$-18.371$&$-18.506$&60&$2\pi\times17$&F2\\\hline
    $y$&-1&$-17.875$&$-18.47$&28&$2\pi\times34$&F1\\\hline
  \end{tabular}
\end{center}
\subsubsection{Group 8}
This group is repeated 10 times.
\begin{center}
  \begin{tabular}{|c|c|c|c|c|c|c|}
    \hline
    Axis&$\Delta n$&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Duration ($\mu$s)& $\Omega_0$ (kHz)&Power ramp\\\hline
    $z$&-2&$-18.371$&$-18.506$&60&$2\pi\times17$&F2\\\hline
    $x$&-1&$-18.03$&$-18.42$&38&$2\pi\times34$&F1\\\hline
    $z$&-1&$-18.4385$&$-18.506$&60&$2\pi\times17$&F2\\\hline
    $y$&-1&$-17.875$&$-18.47$&25&$2\pi\times34$&F1\\\hline
    $z$&-2&$-18.371$&$-18.506$&60&$2\pi\times17$&F2\\\hline
    $x$&-1&$-18.03$&$-18.42$&43&$2\pi\times34$&F1\\\hline
    $z$&-1&$-18.4385$&$-18.506$&60&$2\pi\times17$&F2\\\hline
    $y$&-1&$-17.875$&$-18.47$&28&$2\pi\times34$&F1\\\hline
  \end{tabular}
\end{center}
\subsubsection{Group 9}
This group is repeated 40 times.
\begin{center}
  \begin{tabular}{|c|c|c|c|c|c|c|}
    \hline
    Axis&$\Delta n$&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Duration ($\mu$s)& $\Omega_0$ (kHz)&Power ramp\\\hline
    $z$&-1&$-18.3615$&$-18.429$&70&$2\pi\times9$&F2\\\hline
    $z$&-1&$-18.3615$&$-18.429$&100&$2\pi\times9$&F2\\\hline
    $x$&-1&$-18.03$&$-18.42$&38&$2\pi\times34$&F1\\\hline
    $z$&-1&$-18.3615$&$-18.429$&70&$2\pi\times9$&F2\\\hline
    $z$&-1&$-18.3615$&$-18.429$&100&$2\pi\times9$&F2\\\hline
    $y$&-1&$-17.875$&$-18.47$&25&$2\pi\times34$&F1\\\hline
    $z$&-1&$-18.3615$&$-18.429$&70&$2\pi\times9$&F2\\\hline
    $z$&-1&$-18.3615$&$-18.429$&100&$2\pi\times9$&F2\\\hline
    $x$&-1&$-18.03$&$-18.42$&43&$2\pi\times34$&F1\\\hline
    $z$&-1&$-18.3615$&$-18.429$&70&$2\pi\times9$&F2\\\hline
    $z$&-1&$-18.3615$&$-18.429$&100&$2\pi\times9$&F2\\\hline
    $y$&-1&$-17.875$&$-18.47$&28&$2\pi\times34$&F1\\\hline
  \end{tabular}
\end{center}

>>>>

\section{Raman Sideband Cooling Pulse Parameters and Sequence}
Here, we list the full Raman sideband cooling (RSC) pulse parameters and sequence used to obtain the result in the manuscript.
A step of RSC contains a Raman pulse and an optical pumping pulse.
The full RSC sequence includes 540 pulses in 53 ms.

\subsection{Optical pumping parameters}
The optical pumping is performed with a $\sigma^+$-polarized beam aligned with an 8.8 G bias magnetic field.
There are two frequencies in the beam: one is on resonance with
the $|F=2,m_F=1\rangle$ of $3^2S_{1/2}$ to $|F'=2,m_{F'}=2\rangle$ of $3^2P_{1/2}$ D1 transition
and the other is on resonance with the $|F=1,m_F=1\rangle$ of $3^2S_{1/2}$ to $|F'=2,m_{F'}=2\rangle$ of $3^2P_{3/2}$ D2 transition.
All optical pumping pulses have the length of $30\,\mu$s
with a scattering rate of $0.14$ MHz for atoms in $|F=1,m_F=1\rangle$
and a scattering rate of $0.39$ MHz for atoms in $|F=2,m_F=1\rangle$.

\subsection{Raman pulse parameters}
Each Raman pulse in the cooling sequence is followed immediately by an optical pumping pulse.
The full parameters for the Raman pulses, including the cooling ``axis'',
the sideband ``order ($\Delta n$)'', the cooling frequency ``$\delta '$",
the carrier ($\Delta n=0$) frequency ``$\delta_0'$'', the pulse ``duration'',
the pulse strength in ``$\Omega_0$'',
and the beam of which a non-uniform ``power ramp'' is applied, are listed in 6 groups below.
The applied cooling frequency, $\delta'$,
is the two-photon detuning given relative to the zero-field $F=1$ and $F=2$ hyperfine splitting
of $1.7716261288(10)$GHz~\cite{SteckNa}.
Due to the Stark shifts of the Raman beams, the carrier transition, $\delta'_0$,
varies with the power of the Raman beams.
$\delta'_0$ is given also relative to the zero-field hyperfine splitting.
The strength of the pulses given in $\Omega_0$ determines the two-photon Rabi frequency,
$\Omega_{n,\Delta n}=\Omega_0 \langle n|e^{i \vec{k} \cdot \vec{r}}|n+\Delta n\rangle$.
We adopt the convention that a $\pi$-pulse between state $n$ and $n+\Delta n$ requires a duration $\pi/\Omega_{n,\Delta n}$.
The difference between $\delta'$ and $\delta'_0$ gives the motional sideband frequency, $\delta$.
Many Raman pulses include a ``power ramp'' with a Blackman envelope~\cite{Kasevich1992} to minimize off-resonant excitations.
Because each Raman pulse is a product of two spatial- and temporal-overlapped laser beams,
the ``power ramp'' is applied only to the beam that has the smaller light shift
(we label the beam by the corresponding $F$ number) while the other beam has a square-pulse shape.
For a Raman pulse with a power ramp,
the Rabi frequency gives the arithmetic mean over the duration of the pulse.

\newpage

\subsubsection{Group 1}
This group is repeated 4 times.
\begin{center}
  \begin{tabular}{|c|c|c|c|c|c|c|}
    \hline
    Axis&$\Delta n$&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Duration ($\mu$s)& $\Omega_0$ (kHz)&Power ramp\\\hline
    $x$&-2&$19.625$&$18.649$&44.1&$2\pi\times23$&F1\\\hline
    $y$&-2&$19.615$&$18.648$&28.6&$2\pi\times35$&F1\\\hline
    $x$&-1&$19.130$&$18.649$&36.9&$2\pi\times23$&F1\\\hline
    $y$&-1&$19.615$&$18.648$&24.0&$2\pi\times35$&F1\\\hline
  \end{tabular}
\end{center}

\subsubsection{Group 2}
This group is repeated 5 times.
\begin{center}
  \begin{tabular}{|c|c|c|c|c|c|c|}
    \hline
    Axis&$\Delta n$&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Duration ($\mu$s)& $\Omega_0$ (kHz)&Power ramp\\\hline
    $z$&-5&$19.030$&$18.605$&81.5&$2\pi\times16$&F2\\\hline
    $x$&-2&$19.625$&$18.649$&44.1&$2\pi\times23$&F1\\\hline
    $z$&-4&$18.940$&$18.605$&76.3&$2\pi\times16$&F2\\\hline
    $y$&-2&$19.615$&$18.648$&28.6&$2\pi\times35$&F1\\\hline
    $z$&-5&$19.030$&$18.605$&81.5&$2\pi\times16$&F2\\\hline
    $x$&-1&$19.130$&$18.649$&36.9&$2\pi\times23$&F1\\\hline
    $z$&-4&$18.940$&$18.605$&76.3&$2\pi\times16$&F2\\\hline
    $y$&-1&$19.130$&$18.648$&24.0&$2\pi\times35$&F1\\\hline
  \end{tabular}
\end{center}
\subsubsection{Group 3}
This group is repeated 6 times.
\begin{center}
  \begin{tabular}{|c|c|c|c|c|c|c|}
    \hline
    Axis&$\Delta n$&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Duration ($\mu$s)& $\Omega_0$ (kHz)&Power ramp\\\hline
    $z$&-4&$18.940$&$18.605$&76.3&$2\pi\times16$&F2\\\hline
    $x$&-2&$19.625$&$18.649$&44.1&$2\pi\times23$&F1\\\hline
    $z$&-3&$18.858$&$18.605$&70.2&$2\pi\times16$&F2\\\hline
    $y$&-2&$19.615$&$18.648$&28.6&$2\pi\times35$&F1\\\hline
    $z$&-4&$18.940$&$18.605$&76.3&$2\pi\times16$&F2\\\hline
    $x$&-1&$19.130$&$18.649$&36.9&$2\pi\times23$&F1\\\hline
    $z$&-3&$18.858$&$18.605$&70.2&$2\pi\times16$&F2\\\hline
    $y$&-1&$19.130$&$18.648$&24.0&$2\pi\times35$&F1\\\hline
  \end{tabular}
\end{center}

\newpage
\subsubsection{Group 4}
This group is repeated 7 times.
\begin{center}
  \begin{tabular}{|c|c|c|c|c|c|c|}
    \hline
    Axis&$\Delta n$&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Duration ($\mu$s)& $\Omega_0$ (kHz)&Power ramp\\\hline
    $z$&-3&$18.858$&$18.605$&70.2&$2\pi\times16$&F2\\\hline
    $x$&-2&$19.625$&$18.649$&44.1&$2\pi\times23$&F1\\\hline
    $z$&-2&$18.773$&$18.605$&62.7&$2\pi\times16$&F2\\\hline
    $y$&-2&$19.615$&$18.648$&28.6&$2\pi\times35$&F1\\\hline
    $z$&-3&$18.858$&$18.605$&70.2&$2\pi\times16$&F2\\\hline
    $x$&-1&$19.130$&$18.649$&36.9&$2\pi\times23$&F1\\\hline
    $z$&-2&$18.773$&$18.605$&62.7&$2\pi\times16$&F2\\\hline
    $y$&-1&$19.130$&$18.648$&24.0&$2\pi\times35$&F1\\\hline
  \end{tabular}
\end{center}
\subsubsection{Group 5}
This group is repeated 10 times.
\begin{center}
  \begin{tabular}{|c|c|c|c|c|c|c|}
    \hline
    Axis&$\Delta n$&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Duration ($\mu$s)& $\Omega_0$ (kHz)&Power ramp\\\hline
    $z$&-2&$18.773$&$18.605$&62.7&$2\pi\times16$&F2\\\hline
    $x$&-1&$19.130$&$18.649$&36.9&$2\pi\times23$&F1\\\hline
    $z$&-1&$18.685$&$18.605$&52.5&$2\pi\times16$&F2\\\hline
    $y$&-1&$19.130$&$18.648$&24.0&$2\pi\times35$&F1\\\hline
    $z$&-2&$18.773$&$18.605$&62.7&$2\pi\times16$&F2\\\hline
    $x$&-1&$19.130$&$18.649$&70.0&$2\pi\times23$&F1\\\hline
    $z$&-1&$18.685$&$18.605$&52.5&$2\pi\times16$&F2\\\hline
    $y$&-1&$19.130$&$18.648$&46.0&$2\pi\times35$&F1\\\hline
  \end{tabular}
\end{center}
\subsubsection{Group 6}
This group is repeated 30 times.
\begin{center}
  \begin{tabular}{|c|c|c|c|c|c|c|}
    \hline
    Axis&$\Delta n$&$\delta'$ (MHz)&$\delta'_0$ (MHz)&Duration ($\mu$s)& $\Omega_0$ (kHz)&Power ramp\\\hline
    $z$&-1&$18.683$&$18.605$&78.7&$2\pi\times11$&F2\\\hline
    $z$&-1&$18.683$&$18.605$&135.0&$2\pi\times11$&F2\\\hline
    $z$&-1&$18.685$&$18.605$&78.7&$2\pi\times11$&F2\\\hline
    $x$&-1&$19.130$&$18.649$&36.9&$2\pi\times23$&F1\\\hline
    $y$&-1&$19.130$&$18.648$&24.0&$2\pi\times35$&F1\\\hline
    $z$&-1&$18.685$&$18.605$&78.7&$2\pi\times11$&F2\\\hline
    $z$&-1&$18.685$&$18.605$&135.0&$2\pi\times11$&F2\\\hline
    $z$&-1&$18.685$&$18.605$&78.7&$2\pi\times11$&F2\\\hline
    $x$&-1&$19.130$&$18.649$&70.0&$2\pi\times23$&F1\\\hline
    $y$&-1&$19.130$&$18.648$&46.0&$2\pi\times35$&F1\\\hline
  \end{tabular}
\end{center}
